Using DIT to simplify the DBF feasibility test

### 2013-07-18 dit-paper.tex
Added details on removing redundancy Notation consistency Made a title smaller (to save internet trees)

\section{The demand-bound function feasibility test}
\label{sct:DBF}

@@

Starting from the definition, it remains to find a method to compute the values of $h_i(t)$. In the synchronous case, these values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} : k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k = 1$ to the second task, etc. The maximal value of $k$ can be explicitly stated by rearranging the condition:
$$k T_i + D_i \leq t$$
$$\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor$$
The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$. If this value is negative, it means that no job of task $\tau_i$ respects the condition, i.e. $h_i(t) = 0$. Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\

@@

While redundant equations are not a problem in theory, a short description is always preferred as it can greatly reduce computation times. As was shown previously, the equations corresponding to job deadlines are necessary and sufficient to test the feasibility, so only those can be considered. In \cite{lipariaverage}, the authors use the simplex algorithms to further reduce the number of equation to consider.\\

>>>>

\section{The DBF feasibility test}
\label{sct:DBF}

@@

Starting from the definition, it remains to find a method to compute the values of $h_i(0, t)$ (noted $h_i(t)$ from now on). In the synchronous case, these values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} : k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k = 1$ to the second task, etc. The maximal value of $k$ can be explicitly stated by rearranging the condition:
$$k T_i + D_i \leq t$$
$$\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor$$
The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$. If this value is negative, it means that no job of task $\tau_i$ respects the condition, i.e. $h_i(t) = 0$. Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\

@@

\subsection{Removing redundancy}

While redundant equations are not a problem in theory, a short description is always preferred as it can greatly reduce computation times.\\

As was shown previously, the equations corresponding to job deadlines happening before $H$ are necessary and sufficient to test the feasibility, so only those can be considered. For constrained deadline systems, the end of the first busy period has been proven to be an acceptable upper limit for the DBF test as well, but this value depends on the $C_i$ and therefore cannot be used. In section \ref{sct:DIT}, a similar concept which does not depend on the value of $C_i$ is presented.

In \cite{lipariaverage}, the authors use the simplex algorithm to further reduce the number of equation to consider.\\
